---
title: "Week 9"
author: "Sadie Trombley"
date: "March 5, 2019"
output:
  html_document: default
  pdf_document: default
---


Delete everything besides above when opening new Rmarkdown document 

**This is bold** *This is italic*

##This will make the font bigger
###This will make it slightly smaller 

can google search Rmarkdown cheat sheet
see settings tab in above pane, and knit specifies html vs whatever else, html only exists online
can knit to PDF 
hit ctrl alt i to add a place for r code 
Have to install packages in console rather than in Rmarkdown, but load library here? as seen below in Rcoding section
If we want to get rid of all the coding add warning=FALSE, message=FALSE, and echo=FALSE
Always save before knitting 
```{r, warning=FALSE, message=FALSE}
library(tidyverse)

glimpse(storms)

library(viridis)

ggplot(data=storms)+
  geom_jitter(aes(x= as.factor(month), y = pressure, fill=wind), pch= 21, alpha=.05)+
  scale_fill_viridis_c()+
  theme_bw()+
  labs(title= "Hurrican Pressure V Month", subtitle = "with Max Wind Speed", X = "Month")


```

writing out equations in Rmarkdown:

If you want to write and equation, you put a $ on either side of it.

$\sum_{i=y}^n X_i$

```{r}
library(knitr)
kable(head(storms), caption= "Table using Kable")


htmlTable::htmlTable(head(storms))

#make an interactive table

DT::datatable(storms)

```

```{r}
library(plotly)

ggplotly(
ggplot(data=storms)+
  geom_jitter(aes(x= as.factor(month), y = pressure, fill=wind), pch= 21, alpha= .05)+
  scale_fill_viridis_c()+
  theme_bw()+
  labs(title= "Hurricane Pressure v Month", subtitle = "with Max Wind Speed", x = "Month")
)



```




























